---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# TVQRLB: Quantile Regression Model with Time-Varying Covariates under Length-Biased Sampling

The __TVQRLB__ package implements the estimation and inference procedure for the quantile regression model 
which is based on an estimating equation, with time-varying covariates under length-biased 
sampling scheme.

## Installation

You can install the released version of TVQRLB from [CRAN](https://CRAN.R-project.org) with:

```{r install, eval = FALSE}
install.packages("TVQRLB")
library(TVQRLB)
```

* There will be a GitHub repository for installation soon.

## Example

This is a basic example with some simulation data:

```{r example}
library(survival)
library(TVQRLB)
TVQRLB(fixedCP.cen20, c(-1, 0.5, 1.5), 100, 0.5)
```

## Reference

Cai, Z. and Sit, T. (2018+), "Quantile regression model with time-varying covariates under length-biased sampling," 
*Working Paper*.
