---
title: "Quantile Regression with Time-Varying Covariates under Length-Biased Sampling using TVQRLB"
author: "Zexi Cai, Tony Sit"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo=FALSE}
library(TVQRLB)
```

## Vignette Info

In this vignette, we demonstrate the usage of the `TVQRLB` package, or specifically the `TVQRLB` function
and the `TVQRLB_OP` function.

## Some Simulation Data

The simulated data are generated according to the following formula
$$\tau = \int_0^{T^{*}} \exp( (-1) X_0(t) + (0.5) X_1(t) + (1.5) X_2(t) ) \,dt$$
where the regression level is set to be $0.5$, $\boldsymbol{\beta} = (-1,0.5,1.5)^\top$, and the time dependent covariates are defined as $X_0(t) \equiv 1$, $X_1(t) = (Z_1 + \epsilon_1) \mathbb{I}\{W_1 \leq t < W_2\}$, and $X_2(t) = (Z_2 + \epsilon_2) \mathbb{I}\{t \geq W_2\}$. The instrumental variables are provided by $Z_1$ and $Z_2$ which follow an exponential distribution with unit mean, and the nuisances are obtained from a gamma distribution with shape $4$ and scale $0.4$.

To collect length-biased samples, we generate the truncation variables $A$ from $\mathrm{Unif}(0, a)$ and we keep those samples with $A < T^{*}$, which are then the length-biased failure time $T$. To ensure the length-biasness, $a$ is chosen such that $\mathbb{P}\{T = t \mid T \geq A\} = 0$ for $t > a$, i.e., $a$ is greater than the upper bound of $T$. Censoring times are also obtained from a uniform distribution $\mathrm{Unif}(0, c)$ to yield a desired censoring rate.

In the data with prefix `fixedCP`, the change points are set fixed as $W_1=0.6$ and $W_2=0.9$.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(round(fixedCP.cen20, 4), 10))
```

In the data with prefix `exponCP`, the change points $W_1$ is set to be exponentially distributed with rate $1$, and $W_2$ adds another $\exp(2)$ to $W_1$ so that $W_2$ is always greater than $W_1$.
```{r, echo=FALSE, results='asis'}
knitr::kable(head(round(exponCP.cen20, 4), 10))
```

## Usage of Functions

We fit the model to the data `fixedCP.cen20`, using the standard multiplier bootstrap method for inference:

```{r}
TVQRLB(dataset = fixedCP.cen20, betao = c(-1, 0.5, 1.5), bootstrap_time = 100, qtile = 0.5)
```

Second we fit the model to the same data using the OP method for inference:

```{r}
TVQRLB_OP(dataset = fixedCP.cen20, betao = c(-1, 0.5, 1.5), bootstrap_time = 1000, qtile = 0.5, B_size = 10000)
```

The results are displayed as plain text and returned implicitly as a list of lists.
